\chapter{Acknowledgements}
\label{ack}

Firstly, I would like to give my thanks to my promotors Prof. Boudewijn and Prof. Marius, as well as my supervisors Dr. Berend C. Stoel. Thank you for providing me with the position in LKEB. LKEB is a warm, international, and cooperative lab.

Berend, I feel very lucky and nice to have you as my supervisor. 

Marius,

I appreciate that I met so many friendly colleagues in LKEB. 
Zhiwei, thank you for helping me gradually adapt to life in the Netherlands. Thank you for picking me up at the airport and inviting me for gathering dinner seveval times. You also helped me a lot on technical domain and gave me valuable comments on my projects.
Irene, thank you for your detailed discussion on weekly meeting. I also appreciated the several afternoons walking with you.
Xiaowu, thank you for taking me in when I locked myself out so many times. 
Mody, thank you for your active invitations of various academic or non-academic activities.
Li-shin, thank you for helping me to switch from TensorFlow to PyTorch and you helped me a lot on the Challenge and my daily research. I am also happy to play switch, badminton, and tabble tennis with you.
Michèle, thank you for the help on the development and maintenance of \textit{shark\_resource\_usage} and other IT support. I also very appreciate for your emotional support (you always have a lot of jokes). 
Bo, I am lucky to have you as my roommate. Not only did you help me in my academic and job search process, but you also brought me a lot of happiness in daily life. 
Denis, thank you for your help on the use of MeVisLab. 
Victor, thank you for your help on the organization of Thursday's AI Meeting. 
Patrick, thank you for your sharing of MLflow and your daily lunch invitation. 
Yanli, Xiaotong, and , thank you for your discussion about your or my projects which inspired me a lot. 
Els, thank your for your work on the time-consuming pixel-wise annotation of lobe segmentation masks.
Thanks to Yunjie, Ruochen, Donghang, Qiuyu, Chang, Niels, Jeroen, Mohamed, Baldur, Alexander, Chinmay, Laurens, Simon, Vincent, Silvia, Tahereh, Jouke, Qian, 

I also would like to thank my cooperators from clinical domain. Lucia, Anne, Jeska and Julie, thank you for the support on the SSc scoring project. Emiel and Maarten, thank you for your support on the PFTs estimation project.

I also thank my teachers in China. Prof. Haibin Xue, thank you for writing recommendation letter for my PhD application. I really like your special teaching style in Atomic Physics, which triggered my interest in scientific research. Prof. Yi Wang, it is my honor to be your first student. Your helped me open the door to AI research and you also wrote recommendation letter for my PhD application.

I would also like to thank my dear friends. Kevin, thank your for guiding and supervising my workout. It is a wonderful experience to travel to Ghent and enjoy bars there with you, Brian and Jordi. Thanks to Wensen, Ling, Ningning, Chenhong, Siyi, Ruilin, Youliang, and other Chinese friends in Leiden. We cooked, traveled and played games together. I give my thanks to Zhixi, Shuangrong, Sipu, Jinlei and other friends in China. You gave me emotional support remotely. I want to thank Huijie Liu, who supported me financially during my bachelor's study. I also want to thank China Scholarship Council for supporting me financially during my PhD study.

I would like to thank my families. 感谢爸爸妈妈多年的辛苦付出；感谢弟弟、敏敏和妹妹的关心以及对父母的照顾；感谢可爱的小侄子豪豪带给我快乐；感谢二姨以及其他姨姨姑姑等亲友们多年的帮助和支持。Finally, I want to give my unique thanks to my girlfriend Wenqing. Thank you for your love. I could not arrive here without you.

