\chapter{Publications}

\section*{Journal articles}

\noindent
\textbf{Jia, Jingnan}, Emiel R. Marges, Jeska K. De Vries-Bouwstra, Maarten K. Ninaber, Lucia JM Kroft, Anne A. Schouffoer, Marius Staring, and Berend C. Stoel. "Automatic Pulmonary Function Estimation From Chest CT Scans Using Deep Regression Neural Networks: The Relation Between Structure and Function in Systemic Sclerosis." \textit{IEEE Access} 11 (2023): 135272-135282. 
\bigskip

\noindent
\textbf{Jia, Jingnan}, Irene Hernández-Girón, Anne A. Schouffoer, Jeska K. De Vries-Bouwstra, Maarten K. Ninaber, Julie C. Korving, Marius Staring,  Lucia JM Kroft,  and Berend C. Stoel. "Explainable fully automated CT scoring of systemic sclerosis related interstitial lung disease by cascaded regression neural networks and its comparison with experts." \textit{IEEE Access} (Under review). 
\bigskip

\noindent
Wen, Jingxuan, Yong‐Chang Jiao, Yi‐Xuan Zhang, and \textbf{Jingnan Jia}. "Wideband circularly polarized dielectric resonator antenna loaded with partially reflective surface." \textit{International Journal of RF and Microwave Computer‐Aided Engineering} 29, no. 12 (2019): e21962. 
\bigskip

\section*{Conference proceedings}

\noindent
\textbf{Jia, Jingnan}, Zhiwei Zhai, M. Els Bakker, Irene Hernández-Girón, Marius Staring, and Berend C. Stoel. "Multi-task semi-supervised learning for pulmonary lobe segmentation." In \textit{2021 IEEE 18th International Symposium on Biomedical Imaging (ISBI)}, pp. 1329-1332. IEEE, 2021. 

\bigskip
\noindent
\textbf{Jia, Jingnan}, Marius Staring, Irene Hernández-Girón, Lucia JM Kroft, Anne A. Schouffoer, and Berend C. Stoel. "Prediction of lung CT scores of systemic sclerosis by cascaded regression neural networks." In \textit{Medical Imaging 2022: Computer-Aided Diagnosis}, vol. 12033, pp. 837-843. SPIE, 2022. 

\bigskip

\section*{Open source softwares}

\noindent
\textbf{Jia, Jingnan}. "A package to compute segmentation metrics: seg-metrics." \textit{online at https://pypi. org/project/seg-metrics} (2020). 